---
title: "STAT_308_Project_Code"
author: "Justin Peabody"
date: "2026-04-12"
output: html_document
---

This is a file containing the R code I used to run the regression analyses and generate relevant visualizations for my STAT 308 final project.

```{r}
#To begin, I called the relevant packages and loaded the Kaggle data. 

library(tidyverse)
library(regclass)
Education_data<-read_csv("~/Desktop/STAT 308/Data/StudentPerformanceFactors.csv")


```


```{r}

#I then generated scatterplots of exam scores (the response variable) against each of the 10 predictor variables my group was interested in. Here is one example:

plot(Exam_Score~Hours_Studied, data=Education_data, col=ifelse(Education_data$Exam_Score>=80, "red", "blue"), pch=19)



```

Creatig these plots made it visually clear that the vast majority of the dataset represents exam scores below 80. Only a small cluster of observations correspond to exam scores at or above 80. This motivated our group to split the data into two datasets based on exam score, then generate a separate multiple regression model for each dataset.

```{r}


```

```{rj}
```
